Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-08 doc/paper.tex
work on computational section: numerical results

	\section{Computational Results}
	We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
	\begin{itemize}
		\item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has a higher price. In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.  
		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
		\begin{equation}
		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
		\end{equation}
	\end{itemize}
     We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	 \item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 100 instances per each benchmark set. In overall, we have 200 polygons which vertices with two different weights, which gives us, in overall, 400 problem instances.
     \subsection{Settings and the choice of the Parameters}
      All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB. The maximum computation time of each of our algorithms was set to 5 min.

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
        \end{itemize}  and 6 heuristic approaches: 
           \begin{itemize}
           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$, 
            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
           \end{itemize}
         From our results, we noticed that there is no significant difference between the results of \textsc{Greedy-2} and \textsc{Greedy-3}. Therefore, we report only the results of \textsc{Greedy-2} algorithm.
         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab:t_w0} and Table~\ref{tab:t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively.

         \begin{table}
         \centering
         \begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
         	\hline
         	\multicolumn{5}{|c|}{Avg. results on the topollogically-based benchmarks.} \\
         	\hline
            \multicolumn{1}{|c|}{}&
            \multicolumn{2}{|c|}{$Small$}&
            \multicolumn{2}{|c|}{$Large$} \\
            \hline	
         	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
            \textsc{Cplex} & 15.93 & 0.0 & & \\ \hline
            \textsc{Cp} &  16.04 & 0.0 & & \\ \hline
         	\textsc{Greeedy-1} & 22.04  & & & \\ \hline
         	\textsc{Greeedy-2} & 19.97  & & & \\ \hline
         	\textsc{Greeedy-1 + Cplex} & 18.49 & & & \\ \hline
         	\textsc{Greeedy-2 + Cplex} & 18.39 & & & \\ \hline

         	\hline
         \end{tabular}
         \caption{Different combinations of the algorithms.}
        \end{table}

       \begin{table}
    	\centering
    	\begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
    		\hline
    		\multicolumn{5}{|c|}{Avg. results on the point-based benchmarks.} \\
    		\hline
    		\multicolumn{1}{|c|}{}&
    		\multicolumn{2}{|c|}{$Small$}&
    		\multicolumn{2}{|c|}{$Large$} \\
    		\hline	
    		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
    		\textsc{Cplex} & & & & \\ \hline
    		\textsc{Cp} & & & & \\ \hline
    		\textsc{Greeedy-1} & & & & \\ \hline
    		\textsc{Greeedy-2} & & & & \\ \hline

    		\textsc{Greeedy-1 + Cplex} & & & & \\ \hline
    		\textsc{Greeedy-2 + Cplex} & & & & \\ \hline

    		\hline
    	\end{tabular}
    	\caption{Different combinations of the algorithms.}
    \end{table}
        From the numerical results, we observe the following conclusions:
        \begin{itemize}
        	\item \fxnote{TODO}
        \end{itemize}

>>>>

	\section{Computational Results}
	We used the instance of the specific OAGP up to a 200 vertices, and assigned the weights to each vertex of polygons. We included two kind of weights into these benchmarks:
	\begin{itemize}
		\item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has a higher price. In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.  
		\item \emph{point-based benchmarks:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
		\begin{equation}
		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
		\end{equation}
	\end{itemize}
     We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{small} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	 \item \emph{large} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For small and large instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set. In overall, we have 192 polygons which vertices with two different weights, which gives us, in overall, 384 problem instances.
     \subsection{Settings and the choice of the Parameters}
      All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB. The maximum computation time of each of our algorithms was set to 5 min.

      After conducting preliminary results, we decided to use the following parameters for our algorithms:
      \begin{itemize}
        \item \textsc{Greedy + Cplex} parameters: $K = 0.05 \cdot n$. 
      \end{itemize}
     The benchmark sets and the executable file of our software for this project are provided at \href{link}{link}.
	\subsection{Results and Discussion}
        The following algorithms are included in our computation:
        \begin{itemize}
        	\item  exact approaches: CP and ILP approach.The later is, henceforth, called \textsc{Cplex};
        \end{itemize}  and 6 heuristic approaches: 
           \begin{itemize}
           	\item three pure greedy methods, guided by $g_1$, $g_2$ and $g_3$ greedy criterion. We label them by \textsc{Greedy-1}, \textsc{Greedy-2} and \textsc{Greedy-3}, respectively;
            %\item three \textsc{Greedy+Shaking} variants, henceforth labeled by \textsc{Greedy}-$i$+Shaking, $i=1,2,3$, where $i$ stands for heuristic $g_i$ involved in the method;
            \item three \textsc{Greedy+Cplex} variants, henceforth labeled by  \textsc{Greedy}-$i$+\textsc{Cplex}, $i=1,2,3$, 
            where $i$ stands for heuristic $g_i$ involved as the greedy criterion of the hybrid;
           \end{itemize}
         From our results, we noticed that there is no significant difference between the results of \textsc{Greedy-2} and \textsc{Greedy-3}. Therefore, we report only the results of \textsc{Greedy-2} algorithm.
         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab: t_w0} and Table~\ref{tab: t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively. Each of the tables is additionally  subdivided by a vertical line into two parts, depending on the case if we consider \emph{small} or \emph{large} polygons for a specific weight. 
         For each of the algorithm  we reported average quality and average standard deviation ($\sigma$) over all instances (96 instances) of the considered subgroup. If an asterisk is given, i means taht optimality is proven for all instances of considered subgroup. 
         \begin{table}
         \centering
         \begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
         	\hline
         	\multicolumn{5}{|c|}{Avg. results on the topollogically-based benchmarks.} \\
         	\hline
            \multicolumn{1}{|c|}{}&
            \multicolumn{2}{|c|}{$Small$}&
            \multicolumn{2}{|c|}{$Large$} \\
            \hline	
         	Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
            \textsc{Cplex} & 15.93* & 8.12 & 2.62* & 1.38 \\ \hline
            \textsc{Cp} &  16.04 & 8.24 &  2.62*  & 1.38\\ \hline
         	\textsc{Greeedy-1} & 22.04  & 12.02 & 3.38   & 1.59 \\ \hline
         	\textsc{Greeedy-2} & 19.97  & 9.60  &  3.51 & 1.80\\ \hline
         	\textsc{Greeedy-1 + Cplex}  & 18.49 &  9.56  & 3.34 & 1.41 \\ \hline
         	\textsc{Greeedy-2 + Cplex}  & 18.39 & 8.96 &  3.32 & 1.29 \\ \hline

         	\hline
         \end{tabular}
         \caption{Results of different combinations of the algorithms.} \label{tab: t_w0}
        \end{table}

       \begin{table}
    	\centering
    	\begin{tabular}{ |p{4cm}|p{1.5cm}p{1cm}|p{1.5cm} p{1cm} |  }
    		\hline
    		\multicolumn{5}{|c|}{Avg. results on the point-based benchmarks.} \\
    		\hline
    		\multicolumn{1}{|c|}{}&
    		\multicolumn{2}{|c|}{$Small$}&
    		\multicolumn{2}{|c|}{$Large$} \\
    		\hline	
    		Algorithm  & $|\bar{s}|$ & $\bar{\sigma}$ & $|\bar{s}|$ & $\bar{\sigma}$  \\ \hline \hline
    		\textsc{Cplex} & 36.03* & 19.04 & 6.72* & 3.07 \\ \hline
    		\textsc{Cp} & 36.03* & 19.04 & 6.72* &  3.07 \\ \hline
    		\textsc{Greeedy-1} &39.28  & 19.55 & 6.76 & 3.06 \\ \hline
    		\textsc{Greeedy-2} & 40.92 & 19.54 & 6.76 & 3.06 \\ \hline
    		\textsc{Greeedy-1 + Cplex} & 37.78 & 19.59 &  6.72 & 3.07 \\ \hline
    		\textsc{Greeedy-2 + Cplex} & 37.31 & 19.13 &  6.72 & 3.07 \\ \hline

    		\hline
    	\end{tabular}
    	\caption{Result of different combinations of the algorithms.} \label{tab: t_w1}
    \end{table}
        From the numerical results, we observe the following conclusions:
        \begin{itemize}
        	\item  For the topollogically--based benchmarks and the exact approaches, \textsc{Cplex} achieved best results among other approaches. moreover, Cplex could prove optimallity of all (192) instances, while \textsc{Cp} could not. It is expecially noticed for small polygons, where it seems hard for \textsc{Cp} to prove optimality. 
        	\item For the point--based benchmark set and the exact approaches, \textsc{Cplex} again show its power, since it could prove all instances to optimallity, which is also the case of \textsc{Cp}. 
        	\item  For the topollogically--based benchmarks and the heuristic approaches\fxnote{TODO...}
        \end{itemize} 
          \fxnote{TODO: generisati plotove za vremena svakog od algoritama (da se vidi da je greedy brzi -- nadamo se)}
